---
title: "Marketing Analytics Course 1 module 4"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

First, we upload our times series data.

```{r}
realdata.df <- read.csv("edx_datavis_time.csv", header=TRUE)
```

We check our upload by doing a summary of our data

```{r}
summary(realdata.df)
```

We create a valuables year and price and assign the year and price columns to them.

```{r}
year <- realdata.df$Year
price <- realdata.df$Price1000
```
 
Here we do a simple line plot in red of year and data

```{r}
plot(year, price, type="l", col="red", main="Price Trend", xlab="Year", ylab="Price * 1000")
```

Now we do a bar plot. Bar plots are useful for comparing statistics of one variable. 

```{r}
data.df <- read.csv ("edx_rbasics__1_.csv", header =TRUE)
```

We summarize to check if that data was read in correctly.

```{r}
summary(data.df)
```

We are going to use an aggregate function to find the mean for all the prices of different bedrooms.

```{r}
chartdata <- aggregate (data.df$Price1000, by=list (data.df$Bedrooms), FUN=mean)
```

We print the chartdata to see the mean of all the different houses by the number of bedrooms that they have. 

```{r}
chartdata
```

Now we create names for our chartdata chart.

```{r}
names (chartdata) <- c("Bedrooms", "MeanPrice")
```

We print with our labeled columns.

```{r}
chartdata
```

We then create a bar plot with our chartdata.

```{r}
barplot (chartdata$MeanPrice, names.arg=chartdata$Bedrooms, xlab="Bedrooms", ylab="MeanPrice", col="blue")
```

## Scatterplots are useful for finding relationships between two variables. 

We assign the two variables we'd like to compare. LotAcre to lot and SizeSqFt to house. 

```{r}
lot <- data.df$LotAcre
house <- data.df$SizeSqFt
```

We will now print both lot and house columns

```{r}
lot
```
```{r}
house
```

Here is our of house size versus Lot Size scatter plot.

```{r}
plot(lot, house, col="red", main="House Size vs. Lot Size")
```

We interpret the chart and see that there is a linear and clustering relationship that does suggest that there is a small correlation between the house size and lot size. After five thousand feet there are large outliers and the relationship between lot size and house size decreases.